\begin{frame}[plain, shrink=25]{Occupational Safety and Health Act 9, 2006 and Eye Health}
    \begin{multicols}{2}

        \begin{itemize}
            \item \textbf{Introduction to the OSH Act:}
            \begin{itemize}
                \item The OSH Act 9, 2006 provides a legal framework for workplace safety and health.
                \item Eye health is a critical aspect protected under this Act.
            \end{itemize}
            
            \item \textbf{Relevant Sections for Eye Health:}
            \begin{itemize}
                \item \textbf{Section 92 - Protection of Eyes:} 
                \begin{itemize}
                    \item Mandates provision of protective eyewear for hazardous processes.
                \end{itemize}
                \item \textbf{Section 13 - Training Requirements:} 
                \begin{itemize}
                    \item Employees must be trained on proper use of protective equipment.
                \end{itemize}
                \item \textbf{Section 35 - Duties of Employees:} 
                \begin{itemize}
                    \item Employees must use protective equipment properly and responsibly.
                \end{itemize}
            \end{itemize}
    
            \item \textbf{Case Studies:}
            \begin{itemize}
                \item Examples of workplace incidents where non-compliance led to eye injuries.
            \end{itemize}
            
            \item \textbf{Compliance and Best Practices:}
            \begin{itemize}
                \item Employers should ensure compliance to protect eye health.
                \item Regular inspections and maintenance of protective gear are essential.
            \end{itemize}
            
            \item \textbf{Conclusion:}
            \begin{itemize}
                \item Reiterate legal obligations and the moral duty to protect employee vision.
            \end{itemize}
        \end{itemize}

    \end{multicols}
        

\end{frame}
