\section{IRB Approval Letter}



\begin{letter}{Research and Ethics Committee \\
Faculty of Health Sciences \\
[Institution Name] \\
[Address] \\
[City, State, Zip Code]}

\date{\today}

\opening{Dear [Chairman's Name],}

\section*{PERMISSION TO CONDUCT A RESEARCH STUDY}

I, [Your Name], from the [Your Department/Organization], am writing to request your permission to conduct a research study titled: [Title of Your Research Study]. This study is part of the requirements for the approval of my [Degree Name and Program] at [Your University's Name], [City, Country].

The objective of this research study is [Briefly describe the objective and purpose of your research study].

I assure you that the study will adhere to all ethical guidelines and regulations, and the privacy and confidentiality of participants will be strictly maintained. Additionally, any data collected will be used solely for research purposes and will not be disclosed to any unauthorized individuals or organizations.

Your approval for this research study would greatly contribute to the advancement of knowledge in the field of [Your Field/Area of Study], and I am committed to conducting the study with the highest level of professionalism and integrity.

Thank you for considering my request. I look forward to receiving your approval to proceed with the research study.

\closing{Yours sincerely,}

\end{letter}




\section{Authorization Letter  From Lapaire Uganda}

\begin{letter}{Lapaire Uganda \\
[Address] \\
[City, Country]}

\date{\today}

\opening{Dear Sir/Madam,}

\section*{REQUEST FOR COLLABORATION}

I am writing to you from [Your Institution/Department] with a proposal for collaboration between our organizations. We have been impressed by the quality of service and commitment to eye care provided by Lapaire Uganda and believe that working together could bring mutual benefits.

Our proposal involves [Briefly describe the nature of the collaboration you are proposing, such as research partnership, community outreach programs, or joint initiatives].

We have identified several areas where our organizations could complement each other's strengths and expertise, including [List specific areas of collaboration, such as data sharing, joint research projects, or co-hosting events].

We are confident that a partnership between our organizations would not only enhance the quality of eye care services but also contribute to the advancement of knowledge and innovation in the field.

We would be grateful for the opportunity to discuss this proposal with you further and explore ways in which we can collaborate effectively. Please let us know if you would be interested in meeting to discuss this matter in more detail.

Thank you for considering our proposal. We look forward to the possibility of working together to improve eye care services in Uganda.

\closing{Yours sincerely,}





\section{Authorization Letter 2}

